---
title: "Homework 5"
author: "Shina Min"
date: "11.14.2023"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


### Problem 0

This "problem" focuses on structure of your submission, especially the use git and GitHub for reproducibility, R Projects to organize your work, R Markdown to write reproducible reports, relative paths to load data from local files, and reasonable naming structures for your files. This was not prepared as a GitHub repo.

```{r load_libraries}
library(tidyverse)
```


## Problem 1

For this problem, we are interested in data gathered and made public by _The Washington Post_ on homicides in 50 large U.S. cities. The code chunk below imports and cleans the data.

```{r}
homicide_df = 
  read_csv("data-homicides-master/homicide-data.csv", na = c("", "NA", "Unknown")) %>%
  mutate(
    city_state = str_c(city, state, sep = ", "),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
  ) %>% 
  filter(city_state != "Tulsa, AL") 
```

The resulting dataframe has `r nrow(homicide_df)` entries, on variables that include the victim name, race, age, and sex; the date the homicide was reported; and the location of the homicide. In cleaning, I created a `city_state` variable that includes both city and state, and a `resolution` variable to indicate whether the case was closed by arrest. I also excluded one entry in Tulsa, AL, which is not a major US city and is most likely a data entry error. 

In the next code chunk, I group within cities and summarize to produce the total number of homicides and the number that are solved. 

```{r}
city_homicide_df = 
  homicide_df %>% 
  select(city_state, disposition, resolution) %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolution == "unsolved"))
```

Focusing only on Baltimore, MD, I can use the `prop.test` and `broom::tidy` functions to obtain an estimate and CI of the proportion of unsolved homicides in that city. The table below shows those values.

```{r}
bmore_test = 
  prop.test(
    x = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_unsolved),
    n = filter(city_homicide_df, city_state == "Baltimore, MD") %>% pull(hom_total)) 

broom::tidy(bmore_test) %>% 
  knitr::kable(digits = 3)
```

Building on this code, I can use functions in the `purrr` package to obtain estimates and CIs for the proportion of unsolved homicides in each city in my dataset. The code below implements this analysis. 

```{r}
test_results = 
  city_homicide_df %>% 
  mutate(
    prop_tests = map2(hom_unsolved, hom_total, \(x, y) prop.test(x = x, n = y)),
    tidy_tests = map(prop_tests, broom::tidy)) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  mutate(city_state = fct_reorder(city_state, estimate))
```

Finally, I make a plot showing the estimate (and CI) of the proportion of unsolved homicides in each city.

```{r}
test_results %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

This figure suggests a very wide range in the rate at which homicides are solved -- Chicago is noticeably high and, given the narrowness of the CI, likely is the location of many homicides. 

## Problem 2




## Loading all the necessary packages
```{r, echo=FALSE}
library(tidyverse)
library(rvest)
library(purrr)
library(dplyr)
library(broom)
library(ggplot2)
```


## A dataframe containing all file names using list.files function
```{r message = FALSE, warning= FALSE}
comb_df = 
  tibble(
    files = list.files("data/"),
    path = str_c("data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>%
  unnest()
```


## Iterating over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
```{r}
tidy_df = comb_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3),
    ID = str_sub(files, 5, 7)) %>%
  pivot_longer(week_1:week_8,names_to = "week", values_to = "observation",names_prefix = "week_") %>%
  mutate(week = as.numeric(week)) %>%
  select(group, ID, week, observation)
```



## Making a spaghetti plot showing observations on each subject over time, and comment on differences between groups.

```{r}
spagetti_plot = tidy_df %>%
  ggplot(aes(x = week, y = observation, color = ID)) +
  geom_line() +
  geom_point() + 
  facet_grid(~group) +
  labs(x = 'Week', y = 'Observation', title = 'Observations on each Subject Over Time')

spagetti_plot
```



## Problem 3

## Loading the samples
```{r}
set.seed(12345)
n = 30
sigma = 5
alpha = 0.05
simulations = 5000
```


## The function below generates 5000 datasets from the model at mu = 0, with the above parameters.
```{r}
sim_test = function(mu){

  sim_data = tibble(rnorm(n = 30, mean = mu, sd = 5))

  sim_data %>%
    t.test() %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}

sim_results = 
  expand_grid(
    mu = 0,
    iter = 1:5000) %>% 
  mutate(t_test_df = map(mu, sim_test)) %>% 
  unnest(t_test_df)
```


## The table below generates 5000 datasets from the model at mu = 1, 2, 3, 4, 5, 6, with the above parameters.
```{r}
sim_results_2 =
  expand_grid(
    mu = 0:6,
    iter = 1:5000) %>%
  mutate(t_test_df_2 = map(mu, sim_test)) %>%
  unnest(t_test_df_2)
```


## Making a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis.
```{r}
sim_results_2 |> 
  group_by(mu) |> 
  summarize(proportion_rejected = sum(p.value < 0.05)/5000) |> 
  ggplot(aes(x = mu, y = proportion_rejected)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Power of the Test vs True Value of μ",
       x = "True μ",
       y = "Power of the test")
```

* Describe the association between effect size and power.


## Make a plot showing the average estimate of μ̂ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ̂ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. Is the sample average of μ̂ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?



